### 2015-05-08 background.tex
update to the table

To counter the above limitations, techniques such as Locksmith~\cite{pratikakis2006locksmith} and RELAY~\cite{voung2007relay} have explored the idea of applying lockset analysis in a static context, using dataflow analysis. In this paper, we present a novel static lockset analysis method that involves generating verification conditions, which are then discharged to a theorem prover.

>>>>

To counter the above limitations, techniques such as Locksmith~\cite{pratikakis2006locksmith} and RELAY~\cite{voung2007relay} have explored the idea of applying lockset analysis in a static context, using dataflow analysis. In this paper, we present a novel symbolic lockset analysis method that involves generating verification conditions, which are then discharged to a theorem prover.
